---
title: "hw1"
author: "Chong Zhang"
date: "September 4, 2018"
output: html_document
---


###Question A
####Please see all the missing values in the analysis of variance table below. The **Total Degree of Freedom** is **21** 
```{r warning=FALSE, message=FALSE}
library(reshape2)
library(dplyr)

Control = c(0.53, 0.36, 0.2, -0.37,-0.6, -0.64,-0.68,-1.27)
Knees = c(0.73, 0.31, 0.03, -0.29, -0.56, -0.96, -1.61, NA)
Eyes = c(-0.78, -0.86, -1.35, -1.48, -1.52, -2.04, -2.83, NA)
raw_data = data.frame(cbind(Control,Knees, Eyes))%>%melt()
colnames(raw_data) = c('Treatment', 'Phase Shift(h)')

model = aov(raw_data$`Phase Shift(h)`~raw_data$Treatment)
summary(model)
```

###Question B
```{r warning=FALSE, message=FALSE}
x = model.tables(model, type = 'mean')
u1 = x$tables$`raw_data$Treatment`[1]
u2 = x$tables$`raw_data$Treatment`[2]
u3 = x$tables$`raw_data$Treatment`[3]
```

#### **u1** is the the mean of phase shift in **Control** group, which is **```r u1```**. **u2** is the the mean of phase shift in **Knees** group, which is **```r u2```**. **u3** is the mean of phase shift in **Eyes** group, which is **```r u3```**.


###Question C
####The **null hypothesis** is all three populations have the same mean: **u1 = u2 = u3**. The **alternative hypothesis** is that **the population means are not all equal**
####(i) Under the H0, the F-test statistic has an **F statistic: 7.289**
####(ii) The p-value of the ANOVA F-test is **0.00447**
```{r warning=FALSE, message=FALSE}
TukeyHSD(x = model, conf.level = 0.95)
```

####(iii) Based on the p-value from the F-test, we can reject the null hypothesis, which means that the population means of thress treatment are not the same. Based on the pair-wise comparison, I find that light treatment on eyes can affect the phase shift, whereas light treatment on knees failed to affect phase shift.