---
title: "HW4 self"
author: "Chong Zhang"
date: "November 9, 2018"
output: html_document
---
###A. Buying a Car
a. What is the formula of the estimated probability for a family to buy a car given its income and the age of the car the family owns?

$Ln(\dfrac{p}{1-p})=-4.739+0.0677*income+0.5986*age$

$p =\dfrac{e^{-4.739+0.0677*income+0.5986*age}}{1+e^{-4.739+0.0677*income+0.5986*age}}$

b. Identify the coefficient for the regressor age and interpret.

**income: 0.06773**
**age: 0.59863**

c. Perform a hypothesis testing procedure for the statistical significance of the regression coefficients corresponding to the income factor. Interpret at alpha = 0.05.

```{r}
z = 0.06773/0.02806
2*pnorm(z,lower.tail = F)
```

d. Estimate the probability that a family with $70,000.00 an income whose oldest car is 4 years old buys a new car in the following year.
**0.916**


e. What can you say about the reliability of the statistical significance of the regression coefficients for this data example? Provide supporting arguments for your answer.
**Both intercept and income are significant, however age is not.**


###B. Simulation Example
a. Analyze the data using Poisson regression; obtain both point estimates and confidence intervals for the regression coefficients. Provide the R output and interpret in relation to the true parameters for the model you generated data from.

```{r cache=TRUE}
x=1:10/10
mu = exp(3+0.2*x)
y = rpois(10, mu)
z = as.data.frame(cbind(y,x))
method = glm(formula = y~x, data = z, family = 'poisson')
fitted(method)
summary(method)
confint(method)
plot(fitted(method), y)
```


b. Repeat the data generation process for 100 times. You can use the for loop in R for repeating the data generation.  Set a seed to 1 before the loop in order to reproduce random numbers.   

```{r, cache=T, message=FALSE, warning=FALSE}
set.seed(1)
intcover = 0
xcover=0

for (i in 1:100){
  N=10
  x=1:N/N
  mu = exp(3+0.2*x)
  y=rpois(N,mu)
  model = glm(y~x,family = 'poisson')
  CI = confint(model,level = 0.95)
  intcover = intcover +(CI[1,1]<3 &CI[1,2]>3)
  xcover = xcover+(CI[2,1]<0.2 & CI[2,2]>0.2)
}
intcover
xcover

```

How many times the estimated confidence intervals include the true parameters? Interpret.
**97 times are included.**

c. Generate data as in part (a) except that this time you will generate with  for . Repeat 100 times. How many times the estimated confidence intervals include the true parameters? Interpret.
```{r cache=TRUE, warning=FALSE, message=FALSE}
set.seed(1)
intcover = 0
xcover=0

for (i in 1:100){
  N=1000
  x=1:N/N
  mu = exp(3+0.2*x)
  y=rpois(N,mu)
  model = glm(y~x,family = 'poisson')
  CI = confint(model,level = 0.95)
  intcover = intcover +(CI[1,1]<3 &CI[1,2]>3)
  xcover = xcover+(CI[2,1]<0.2 & CI[2,2]>0.2)
}
intcover
xcover

```

93 time are included. 

d. Are the answers for part (b) and (c) different? Why?
They are differnt. Because the sample number of part b is not large enough as part c. Possion regression requires large sample size to make acurate statistic inferrence.

