---
title: "HW4 self"
author: "Chong Zhang"
date: "November 9, 2018"
output: html_document
---
###A. Buying a Car
a. What is the formula of the estimated probability for a family to buy a car given its income and the age of the car the family owns?

$Ln(\dfrac{p}{1-p})=-4.739+0.0677*income+0.5986*age$

$p =\dfrac{e^{-4.739+0.0677*income+0.5986*age}}{1+e^{-4.739+0.0677*income+0.5986*age}}$

b. Identify the coefficient for the regressor age and interpret.

**income: 0.06773**
**age: 0.59863**

c. Perform a hypothesis testing procedure for the statistical significance of the regression coefficients corresponding to the income factor. Interpret at alpha = 0.05.

```{r}
p = 0.06773/0.2806
2*pnorm(p)
```

d. Estimate the probability that a family with $70,000.00 an income whose oldest car is 4 years old buys a new car in the following year.

e. What can you say about the reliability of the statistical significance of the regression coefficients for this data example? Provide supporting arguments for your answer.


```{r setup, include=FALSE}



```